-

### 2023-01-20 DRAFT_homogeneous_impact_areas.Rmd
bug: Cache large operation

```{r, eval=F}
# runtime about 30 sec
infra_agg <- st_warp(infra, cellsize = c(1000, 1000), 
                                   crs = st_crs(infra), 
                                   use_gdal = TRUE,
                                   method = "average")
saveRDS(infra_agg, "P:/41201785_okologisk_tilstand_2022_2023/data/cache/infra_agg.rds")
```

```{r, echo=F}
infra_agg <- readRDS("P:/41201785_okologisk_tilstand_2022_2023/data/cache/infra_agg.rds")
```

@@

The CRS needs to be identical 
```{r}
infra_agg <- st_transform(infra_agg, 25833)
```

```{r}
infra_agg_terrestrial <- st_crop(infra_agg, outline)
```

@@

<!-- Continue from here after fixing  ea_homogeneous_area -->
```{r, warning=F}
infra_agg_discrete_vect <- eaTools::ea_homogeneous_area(infra_agg_discrete, groups = infrastructureIndex)
```

@@

```{r}
infra_agg_discrete_vect <- st_transform(infra_agg_discrete_vect, 25833)
```

>>>>

```{r, eval=F}
# runtime about 30 sec
infra_agg <- st_warp(infra, cellsize = c(1000, 1000), 
                                   crs = st_crs(infra), 
                                   use_gdal = TRUE,
                                   method = "average")
# The CRS needs to be identical for st_crop
infra_agg <- st_transform(infra_agg, 25833)
```

@@

```{r, eval=F}
infra_agg_terrestrial <- st_crop(infra_agg, outline)
saveRDS(infra_agg_terrestrial, "P:/41201785_okologisk_tilstand_2022_2023/data/cache/infra_agg_terrestrial.rds")
```

```{r, include=F}
# silently load cached file
infra_agg_terrestrial <- readRDS("P:/41201785_okologisk_tilstand_2022_2023/data/cache/infra_agg.rds")
```

@@

```{r, warning=F}
infra_agg_discrete_vect <- eaTools::ea_homogeneous_area(infra_agg_discrete, groups = infrastructureIndex)
```

@@
